---
title: "Unit 1 - 3 Review Starter"
author: "Team data scientist"
date: "02/23/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)

 names(sites)
```

There are 23 rows and 2 variables.

Each row represents a mineral type found at a particular location.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(location_descriptions)
glimpse(solubility_hardness)

names(density)
names(location_descriptions)
names(solubility_hardness)
```
There are 3 rows and 2 variables in the density data.
There are 10 rows and 2 variables in the location_descriptions data.
There are 3 rows and 3 variables in the solubility_hardness data.

The rows in Solubility_hardness.csv dataset describes the degree of solubility and range of hardness of each mineral.

The rows in the location_descriptions.csv dataset describes the condition of the location where each mineral was found.

The rows in the density.csv dataset describes the density of each mineral type.
### Exercise 3

```{r join-mineral-properties}
sand_minerals_density <- sites %>% left_join(density)

sand_mineral_properties <- sand_minerals_density %>% 
  left_join(solubility_hardness)

```
There are 23 rows and 3 variables. It is the same as the sand_minerals data set. 
### Exercise 4

```{r sand-per-location}
sand_mineral_properties %>% count(location)
```

```{r slice-sand}
sand_mineral_properties %>% slice_tail(n = 10)
```

```{r sand-density}
sand_mineral_properties %>%
  arrange(desc(density)) %>%
  slice_tail(n = 10)
```

```{r select-sand}
sand_mineral_properties %>%
  select(1,5) %>%
  slice_tail(n = 5)
```

```{r remove-hardness-NA}
sand_mineral_properties %>%
  filter(is.na(hardness) != TRUE) %>%
  arrange(desc(density)) %>%
  slice_head(n = 5)
```


### Exercise 5

```{r glimpse density}
glimpse(density)
```

```{r minerals observed}
density %>%
count(minerals)
```

```{r density/1000}
density_1000 <- density %>% 
  mutate(density_1000 = density/1000)
```

```{r density values}
sand_mineral_properties %>%
  summarize(mean_density= mean(density))
  
```
```{r density group by location}
sand_mineral_properties %>%
  group_by(location) %>% 
  summarize(mean_density= mean(density))
```



### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9


```{r homeworld-barplot, fig.height=10, fig.width=10}
starwars %>%
  filter(is.na(gender)==FALSE ) %>% 
  ggplot(aes(x = gender, color = gender)) +
  geom_bar( position = "stack") +
  labs(
    title = "Homeworld-Barplot",
    x = "Gender",
    y = "Count"
  ) +
 facet_wrap(~homeworld)
  
```

There are few homeworld that have both genders with the masculine gender having higher number of characters than the feminine gender. There are homeworld with only female characters and others with male character.
In conclusion, there more masculine homworld than feminine