---
title: "Unit 1 - 3 Review Starter"
author: "Team data scientist"
date: "02/23/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)

 names(sites)
```

There are 23 rows and 2 variables.

Each row represents a mineral type found at a particular location.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(location_descriptions)
glimpse(solubility_hardness)

names(density)
names(location_descriptions)
names(solubility_hardness)
```
There are 3 rows and 2 variables in the density data.
There are 10 rows and 2 variables in the location_descriptions data.
There are 3 rows and 3 variables in the solubility_hardness data.

The rows in Solubility_hardness.csv dataset describes the degree of solubility and range of hardness of each mineral.

The rows in the location_descriptions.csv dataset describes the condition of the location where each mineral was found.

The rows in the density.csv dataset describes the density of each mineral type.
### Exercise 3

```{r join-mineral-properties}
sand_minerals_density <- sites %>% left_join(density)

sand_mineral_properties <- sand_minerals_density %>% 
  left_join(solubility_hardness)

```
There are 23 rows and 3 variables. It is the same as the sand_minerals data set. 
### Exercise 4

```{r sand-per-location}
sand_mineral_properties %>% count(location)
```

```{r slice-sand}
sand_mineral_properties %>% slice_tail(n = 10)
```

```{r sand-density}
sand_mineral_properties %>%
  arrange(desc(density)) %>%
  slice_tail(n = 10)
```

```{r select-sand}
sand_mineral_properties %>%
  select(1,5) %>%
  slice_tail(n = 5)
```

```{r remove-hardness-NA}
sand_mineral_properties %>%
  filter(is.na(hardness) != TRUE) %>%
  arrange(desc(density)) %>%
  slice_head(n = 5)
```


### Exercise 5

```{r glimpse density}
glimpse(density)
```

```{r minerals observed}
density %>%
count(minerals)
```

```{r density/1000}
density_1000 <- density %>% 
  mutate(density_1000 = density/1000)
```

```{r density values}
sand_mineral_properties %>%
  summarize(mean_density= mean(density))
  
```

```{r density group by location}
sand_mineral_properties %>%
  group_by(location) %>% 
  summarize(mean_density= mean(density))
```



### Exercise 6

```{r sand_minerals}
sites %>% 
  pivot_wider(names_from = minerals, values_from = location)
```

```{r sand_minerals 2}
sites %>% 
  pivot_longer(names_to = "locations", values_to = "number", cols = 1,2)
```

```{r sand_mineral_density}
sand_minerals_density %>% 
  pivot_wider(names_from = minerals, values_from = density)
```


## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

```{r starwars-heights}
starwars %>% 
  ggplot(aes(x= height, fill= species))+
  geom_histogram()+
  labs(title= "Star Wars Character Heights", x= "Heights", y= "Years")+
  facet_wrap(~ species)+
  theme_bw()

```
Humans have the highest variability to their heights compared to the other Star Wars species. 


### Exercise 8

```{r weight-vs-height,warning=FALSE}
starwars %>%
  filter(mass <= 1000) %>%
  ggplot(aes(height, mass)) +
  geom_point() +
  labs(x = "Height", y = "Mass", title = "Mass vs. Height of Star Wars characters") +
  geom_smooth() +
  facet_wrap(~homeworld)
  
```


### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
